\section{Iterative PlasBin-flow binning method}\label{sec:pbf_iterbin}

In the following, a fragment can refer to both a pangenome fragment or a contig.
As an abuse of notation, we use in the whole section the set \Fragments{} to denote either the pan-assembly fragment set or the contig set.

The here presented Iterative PlasBin-flow binning method is an adaptation of the original PlasBin-flow method~\cite{manePlasBinflowFlowbasedMILP2023}.

The binning method consists in iteratively find the best bin by solving a flow-based combinatorial optimization problem on a network graph (defined in \Cref{sec:pbf_iterbin:network}).
Once a bin is found, we extract it from the network and continue the search until some criterion are not met.
For a given bin, each fragment is associated with a use of its coverage.
Extracting the bin from the network graph means decreasing the fragment coverages in the graph.
When the coverage a fragment in the network falls to zero, the fragment and its arcs are removed from graph.
\Cref{algo:pbf_iterbin} details the iterative binning process.

\begin{tcbalgo}{Iterative PlasBin-flow binning}{pbf_iterbin}
  \begin{algorithmic}[1]
    \Require{%
      A network graph \(N\) as in \Cref{definition:pbf_iterbin:network_graph}.
    }
    \Ensure{%
      Extract bins from the network graph.
    }
    \Function{extract\_bins}{\( N \)}
    \While{There are seeds in \(N\) and the previous model was feasible}
    \State{} \( find\_result \gets \Call{find\_best\_bin}{ N } \)
    \If{\( find\_result.\Call{feasibility\_message}{  } \) is a feasible message}
    \State{} Output \( find\_result.\Call{bin}{ } \)
    \State{} Extract the bin from the network graph \(N\) by updating the coverages.
    \EndIf{}
    \EndWhile{}
    \EndFunction{}
  \end{algorithmic}
\end{tcbalgo}

We propose three Mixed Integer Linear Programming (MILP) approaches to find the best bin (\( \Call{find\_best\_bin}{} \) subfunction, \Cref{sec:pbf_iterbin:decomp,sec:pbf_iterbin:binlab,sec:pbf_iterbin:once})
Each of them tries to answer to the PlasBin-flow discussion.

\begin{newfeatbox}
  Comparing to PlasBin-flow, we directly model the flow connectivity in the MILP models.
\end{newfeatbox}

The MILP models share subsets of variables and constraints we detail in \Cref{sec:pbf_iterbin:milp}.

%
% Common parts among the approaches
%
\input{pbf_iterbin/network.tex}

\input{pbf_iterbin/milp/_index.tex}

%
% Approaches
%
\input{pbf_iterbin/decomp/_index.tex}

\input{pbf_iterbin/binlab/_index.tex}

\input{pbf_iterbin/once/_index.tex}

%
% Conclusions
%
\input{pbf_iterbin/conclusions.tex}