\subsection{Assembly plasmid binning input data}

\begin{definition}{Contig set}{contig_set}
  Let \Contigs{} be the contig set.
  A contig is a sequence resulting from a read assembly process.
\end{definition}

Each contig is associated with three properties: its coverage, its plasmidness and a list of GC scores depending on GC content intervals.

In the following, \(c \in \Contigs{}\) is a contig.

\begin{definition}{Contig coverage}{contig_coverage}
  By \(\cov{c} \in \Reals_{>0}\) we denote the coverage of \(c\).
  It corresponds to the average base coverage of the contig normalized by the median coverage of the contigs in the whole assembly.
\end{definition}

\begin{definition}{Contig GC score}{contig_GC_score}
  \begin{newfeatbox}
    We do not normalize the probabilities by the sum of the \(P(k|n,l)\) over all \(k \in K\) as in~\cite{manePlasBinflowFlowbasedMILP2023}. We normalize them according to the maximum among them.
  \end{newfeatbox}
  Let \(c \in \Contigs{}\) be a contig and \(k\) be a GC content interval.
  By \(\gcscore{c}{k} \in [-1, 1]\) we denote the GC score of the contig \(c\) according to the GC content interval \(k\):
  \[
    \gcscore{c}{k} = 2 \frac{\Pr(n|k,l)\Pr(k)}{\max\limits_{k' \in K}\Set*{\Pr(n|k',l)\Pr(k')}} - 1
  \]
  Where \(K\) is the set of GC content intervals, \(n\) is the number of GC in the contig of length \(l\), and \(\Pr(n|k,l)\) is calculated as described in~\cite{manePlasBinflowFlowbasedMILP2023}, Section 2.5.1.

  \begin{fixmebox}
    Adapt the correction constraints according to the new score definition.
  \end{fixmebox}

  \begin{questionbox}
    For both performance and interpretation issue, we should not have a negative GC score.
  \end{questionbox}
\end{definition}

\begin{definition}{Contig plasmidness}{contig_plasmidness}
  Let \(c \in \Contigs{}\) be a contig.
  By \(\plm{c} \in [-1, 1]\) we denote its plasmidness score.
  A plasmid sequence classifier can help to provide these scores.
\end{definition}

\begin{definition}{Seed contigs}{seed_contigs}
  The set \(\ContigSeeds{} \subset \Contigs{}\) contains the seed contigs.
  Seed contigs are contigs likely to define one or several bins.
  A bin can contain several seed contigs.
\end{definition}

\begin{definition}{Assembly graph}{assembly_graph}
  Let \(G_{asm} = (V_{\Contigs{}}, A_{\Links{}})\) be an assembly graph, a specific case of the sequence graph (\zcref[S]{definition:sequence_graph_dg}), where:
  \begin{itemize}
    \item The vertex set \(V_{\Contigs{}}\) represents the oriented contigs in \(\Contigs{} \times \Orientations{}\)
    \item The arc set \(A_{\Links{}}\) represents the links between the oriented contigs
  \end{itemize}

\end{definition}