\section{Pangebin method}

\begin{todobox}
  Summarize thanks to an algorithm.
\end{todobox}

\begin{todobox}
  Generalize the idea of coarse-to-fine-grain approach by splitting all the objectives.

  \begin{enumerate}[label=\roman*.]
    \item Find max flow
    \item With flow near to max flow, find best GC score
    \item With flow near to max flow, with GC score near to best GC score, find best gene density
    \item \textbf{[Future]} With blabla, find best plasmid-type subgraph
  \end{enumerate}
\end{todobox}

Pangebin is based on the PlasBin-flow approach~\cite{manePlasBinflowFlowbasedMILP2023} and adapts its method to be applied to pan-assembly graphs.

\begin{newfeatbox}
  At the opposite of PlasBin-flow, we split each objective expression into different mono-objective functions that define different optimization problems.
\end{newfeatbox}

However, Pangebin tackles the binning of the fragments with a coarse-to-fine-grain approach in three stages (each one refering to an optimization problem) iteratively applied on smaller pan-assembly graph:

\begin{enumerate}[label=\roman*.]
  \item Find the maximum coverage flow (\MCF{} problem, \Cref{meth:max_coverage_flow})
  \item Find the maximum GC probability score (\MGC{} problem)
  \item Find the maximum gene density score (\MGD{} problem)
\end{enumerate}

We model these three subproblems as dedicated flow formulations with Mixed Integer Linear Programming (MILP):

\begin{itemize}
  \item To keep the direction of the flow along the link-edges in \(E_\Links{}\), we transform each link-edge to two link-arcs with the function \(etoa \colon \Set*{u, v} \mapsto \Set*{(u, v), (v, u)}\).
  \item We add two vertices, \(s\) and \(t\) that are respectively the source and the sink vertices.
  \item The set \(\VSeed{}\) contains the vertices associated with the seed fragments.
    The source goes into each vertex in \(\VSeed{}\), and each vertex in \(V_t \cup V_h\) goes into the sink.
\end{itemize}

\begin{definition}{Pan-assembly network}{panassembly_network}
  Let \(N = (V, A_\Fragments{} \cup A_\Links{}, s, t, \cov{\Fragments{}}, \gcscore{\Fragments{}}{K}, \gd{\Fragments{}})\) be the pan-assembly network, where:

  \begin{itemize}
    \item \(V = V_t \cup V_h \cup \Set*{s, t}\) is the set of vertices with the source \(s\) and the sink \(t\);
    \item \(A_\Fragments{} = \bigcup_{e \in E_\Fragments{}} etoa(e)\) is the set of fragment-arcs;
    \item \(A_\Links{} = \bigcup_{e \in E_\Links{}} etoa(e) \cup \Set{(s, v) \given v \in \VSeed{}} \cup \Set{(v, t) \given v \in V}\) is the set of link-arcs augmented with the seed-arcs and the sink-arcs;
    \item \(\cov{\Fragments{}} \colon \Fragments{} \to \Reals{}_{> 0}\) is the coverage function;
    \item \(\gcscore{\Fragments{}}{K} \colon \Fragments{} \times K \to [-1, 1]\) is the GC score function;
    \item \(\gd{\Fragments{}} \colon \Fragments{} \to \Reals{}_{\geq 0}\) is the gene density function.
  \end{itemize}
\end{definition}

In what follow, we define either a fragment, a contig or an arc to be \enquote{active} if it participates in the solution, i.e.\ the flow passes through it.

\begin{newfeatbox}
  We model a connected-flow directly in the MILP model.

  \begin{notebox}
    The variables \(x\) are now defined in the vertex set rather than the fragment set.
  \end{notebox}
\end{newfeatbox}

Furthermore, Pangebin answers one of the PlasBin-flow discussion point: we ensure the induced solution subgraph defined by arcs with positive flow is connected.

\begin{todobox}
  Describe the update of the graph between the iterations (for the two problems).

  \begin{enumerate}
    \item reduce the coverage
    \item remove from the contig set the contigs for which one of its fragment has a null coverage
  \end{enumerate}
\end{todobox}

\input{pangebin/mcf}

\input{pangebin/mgc}

\input{pangebin/mgd}

\input{pangebin/fine_tune/_index}

% \input{pangebin/plasmid-properties_guided_flow/_index}
