\subsubsection{Fragment correction attributes}

\begin{fixmebox}
  Because of the new attributes definitions, the corrections introductions and definitions must be adapted.
\end{fixmebox}

\begin{definition}{GC probability score bonus}{frag_gc_bonus}
  \begin{fixmebox}
    The GC penalty become GC prob.\ score: adapt the following definition.
  \end{fixmebox}
  Given a contig \(c \in \Contigs{}\) and a GC content interval \(b \in K\), we define \(\dcgcscore{c}{b}\) as the as a positive GC probability score bonus for the subcontigs of \(c\):
  \[
    \dcgcscore{c}{b} = \max \Set*{
      0,
      \sum_{\substack{
          i \in \Fragments{}(c) \\ i \text{ a subcontig}
      }}
      \parenth*{
        \frac{|i|}{|c|}\gcscore{c}{b} - \gcscore{i}{b}
      }
    }
  \]
  The bonus for the share depends on which contigs they belong.
  Given a share \(j \in \Fragments{}\) and a GC content interval \(b \in K\), we define \(\dsgcscore{j}{c}{b}\) as the positive difference between the GC penalty from the normalization of the fragment penalty according to the contig and the fragment penalty computed independently of the contigs it belongs:
  \[
    \dsgcscore{j}{c}{b} = \max \Set*{
      0,
      \frac{|j|}{|c|} \gcscore{c}{b} - \gcscore{j}{b}
    }
  \]
  \begin{questionbox}
    A real equivalence between a contig and the sequence of its fragments should imply the \enquote{bonus} to be possibly negative.
    How to argue in favour of a positive bonus rather than a real correction?

    Be aware that if the deltas can be negatives, then we must change the associated constraints
  \end{questionbox}
\end{definition}

\begin{ideabox}
  As for a contig \(c\),
  \[
    \gcscore{c}{b} \leq \dcgcscore{c}{b} + \sum_{\substack{
        j \in \Fragments{}(c) \\
        j \text{ is a share}
    }}\dsgcscore{j}{c}{b}
  \]
  If we don't want to count twice the share participations, we should define:
  \[
    \dcgcscore{c}{b} = \max \Set*{
      0,
      \gcscore{c}{b} - \sum_{i \in \Fragments{}(c)} \gcscore{i}{b}
    }
  \]
  and if a better contig is active, remove the share participation of the worst.

  \begin{questionbox}
    What should we not count twice a share participation, while if it is counted twice, it is because it is used several times (a repeat).

    Perhaps the best thing is just to add a bonus (or correct, negatively too)
  \end{questionbox}
\end{ideabox}

\begin{notebox}
  The constraints were written but as the discussions are changing a lot, I don't put them in the doc now (see \url{pangebin/fine_tune/to_sort.tex} file).
\end{notebox}